Datasets used in thesis

### 2014-12-01 Rmarkdown/datasets.Rmd
End of day commit
Added TODO
Complete re-write of the Makefile, which required modifications of all .Rmd files and the main .tex file.
Misc. notes.

## Chapter overview

@@

@@

>>>>

\chapter{Datasets used in thesis}\label{chap:datasets}

\section{Chapter overview}

@@

__TODO: Describe processing of data__

@@

## CpG islands

I have used CpG island definitions from the hidden Markov model proposed by \cite{@Wu:2010do}. These predicted CpG islands were downloaded from [http://rafalab.jhsph.edu/CGI/](http://rafalab.jhsph.edu/CGI/) on 29/10/2014.

## Misc. notes

- `Bis-SNP` run without `--trim5` and `--trim5` flags. This is a bit unfortunate but it was because the `bissnp_easy_usage.pl` script, which I used to run `Bis-SNP`, didn't support these. To re-genotype all samples would have taken too long and it shouldn't greatly affect my analyses.
- Percentage of CpGs that are in Rafa's CGIs
